Correlation Resilience Window

### 2017-12-27 analysis/explore_correlations_windows_size.Rmd
update correlations window size

# Read correlation tables of BAI from: ../analysis/analysis_resilience_bai.md 
# sj 
corBai <- read.csv(file=paste0(di, '/out/correla_resilience/correla_window_size.csv'), header = TRUE)
corEvi <- read.csv(file=paste0(di, '/out/correla_resilience/correla_window_size_evi.csv'), header = TRUE)
```

@@

>>>>

# Read correlation tables of BAI from: ../analysis/analysis_resilience_bai.md 
# sj 
corBai <- read.csv(file=paste0(di, '/out/correla_resilience/correla_window_size.csv'), header = TRUE)
corEvi <- read.csv(file=paste0(di, '/out/correla_resilience/correla_window_size_evi.csv'), header = TRUE)
corRwi <- read.csv(file=paste0(di, '/out/correla_resilience/correla_window_size_rwi.csv'), header = TRUE)
```

@@

# RWI

```{r}
cor_rte <- generaMatrix(corRwi, 'rt')
cor_rce <- generaMatrix(corRwi, 'rc')
cor_rse <- generaMatrix(corRwi, 'rs')
cor_rrse <- generaMatrix(corRwi, 'rrs')
```

```{r}
g_rte <- ggcorrplot(cor_rte, type='upper', lab=TRUE, title='RWI Rt', show.legend = FALSE)
g_rce <- ggcorrplot(cor_rce, type='upper', lab=TRUE, title='RWI Rc', show.legend = FALSE)
g_rse <- ggcorrplot(cor_rse, type='upper', lab=TRUE, title='RWI Rs', show.legend = FALSE)
g_rrse <- ggcorrplot(cor_rrse, type='upper', lab=TRUE, title='RWI RRs', show.legend = TRUE)

```{r correla_window_rwi}
grid.arrange(g_rte, g_rce, g_rse, g_rrse)
```
